Draft2

### 2022-04-20 Draft2.Rmd
tried organizing the countries based on air pollutant type..

>>>>

```{r}
glimpse(deaths_df)

#This is the average of all countries by type of air pollutant death
deaths_df %>% 
  group_by(country) %>% 
  select(indoor_deaths, outdoor_deaths, ozone_deaths) %>% 
  summarize(avg_indoor = mean(indoor_deaths), avg_outdoor = mean(outdoor_deaths), avg_ozone = mean(ozone_deaths))

#Sort descending to see which country had the highest of each...(not sure if this is right)
deaths_df %>% 
  group_by(country) %>% 
  select(indoor_deaths, outdoor_deaths, ozone_deaths) %>% 
  summarize(avg_indoor = mean(indoor_deaths), avg_outdoor = mean(outdoor_deaths), avg_ozone = mean(ozone_deaths)) %>% 
  arrange(desc(avg_indoor), desc(avg_outdoor), desc(avg_ozone))
```
